---
title: "Week 2: Hands-on Exercise"
sidebar: false
pagetitle: "Hands-on Ex 02"
---

::: callout-note
## Disclaimer

Hands-on exercises are for my own practice and are ungraded. Thus, the plots and write-ups may be unrefined and poorly labelled.
:::

```{r, include = FALSE}
pacman::p_load(ggrepel, patchwork, 
               ggthemes, hrbrthemes,
               tidyverse)
```

## Load dataset

```{r}
exam_data <- read_csv("data_02/Exam_data.csv")
```

## Why use `ggrepel`?

When there is a large number of data points, it may become difficult to annotate the graph using traditional `ggplot2`:

::: panel-tabset
#### Plot

```{r, echo = FALSE, message = FALSE}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              linewidth=0.5) +  
  geom_label(aes(label = ID), 
             hjust = .5, 
             vjust = -.5) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              linewidth=0.5) +  
  geom_label(aes(label = ID), 
             hjust = .5, 
             vjust = -.5) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```
:::

To use `ggrepel`, we just need to replace `geom_text()` by `geom_text_repel()` and `geom_label()` by `geom_label_repel()`

## Example of using ggrepel

::: panel-tabset
#### Plot

```{r, echo = FALSE, message = FALSE}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              size=0.5) +  
  geom_label_repel(aes(label = ID), 
                   fontface = "bold") +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              size=0.5) +  
  geom_label_repel(aes(label = ID), 
                   fontface = "bold") +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```
:::

## Themes! Themes! Cool themes! From ggtheme package

While `ggplot2` has some built-in themes such as `theme_gray()`, `theme_bw()`, `theme_classic()`, `theme_dark()`, `theme_light()`, `theme_linedraw()`, `theme_minimal()`, and `theme_void()`, we can also use some cool themes from `ggtheme`.

::: panel-tabset
#### theme_gray()

```{r, echo = FALSE, message = FALSE}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  theme_gray() +
  ggtitle("Distribution of Maths scores") 
```

#### The Economist

```{r, echo = FALSE, message = FALSE}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_economist()
```

#### WSJ

```{r, echo = FALSE, message = FALSE}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_wsj()
```

#### Old Excel

```{r, echo = FALSE, message = FALSE}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_excel()
```
:::

## Using `hrbthemes` package

`hrbthemes` focuses on typographic elements, allowing you to customize label placements and fonts used.

::: panel-tabset
#### Plot

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_ipsum(axis_title_size = 18,
              base_size = 15,
              grid = "Y")
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE, warning = FALSE}
ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  ggtitle("Distribution of Maths scores") +
  theme_ipsum(axis_title_size = 18,
              base_size = 15,
              grid = "")
```
:::

::: callout-tip
## Tips

-   `axis_title_size` alters the font size of the axis title

-   `base_size` messes with the default axis labels

-   `grid` determines whether you see grids. It accepts the following values: TRUE, FALSE, X, x, Y, y, or a combination, i.e., XY
:::

## `patchwork`! Patching multiple graphs together

Imagine that you have multiple graphs:

```{r}
p1 <- ggplot(data=exam_data, 
             aes(x = MATHS)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") + 
  coord_cartesian(xlim=c(0,100)) +
  ggtitle("Distribution of Maths scores")
```

```{r}
p2 <- ggplot(data=exam_data, 
             aes(x = ENGLISH)) +
  geom_histogram(bins=20, 
                 boundary = 100,
                 color="grey25", 
                 fill="grey90") +
  coord_cartesian(xlim=c(0,100)) +
  ggtitle("Distribution of English scores")
```

```{r}
p3 <- ggplot(data=exam_data, 
             aes(x= MATHS, 
                 y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              size=0.5) +  
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100)) +
  ggtitle("English scores versus Maths scores for Primary 3")
```

You can combine two graphs together side by side:

::: panel-tabset
#### Plot

```{r, echo = FALSE, message = FALSE, warning = FALSE}
p1 + p2
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE, warning = FALSE}
p1 + p2
```
:::

Or combine three of them using the following operators:

-   "\|" operator to place the plots side by side

-   "/" operator to stack one on top of another

-   "()" operator the define the sequence of plotting

And also add the following:

-   `plot_annotation()`, which will automatically tag the different figures
-   `inset_element()`, which will add another plot based on your specified position (not demonstrated)

::: panel-tabset
#### Plot

```{r, echo = FALSE, message = FALSE, warning = FALSE}
((p1 / p2) | p3) + 
  plot_annotation(tag_levels = 'A') & theme_economist()
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE, warning = FALSE}
((p1 / p2) | p3) + 
  plot_annotation(tag_levels = 'A') & theme_economist()
```
:::
