---
title: "Week 3: Hands-on Exercise"
sidebar: false
pagetitle: "Hands-on Ex 03"
---

```{r, include = FALSE}
pacman::p_load(ggiraph, plotly, patchwork, DT, tidyverse)
```

## Load dataset

```{r}
exam_data <- read_csv("data_03/Exam_data.csv")
```

`ggiraph` is a `ggplot2` extension that can allow plots to become interactive. Three arguments are accepted:

-   Tooltip

-   Onclick

-   Data_id

Its usage will be demonstrated via the example code chunks below.

## Tooltip aesthetic

```{r}
exam_data$tooltip <- c(paste0(     
  "Name = ", exam_data$ID,         
  "\n Class = ", exam_data$CLASS))

p <- ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_dotplot_interactive(
    aes(tooltip = exam_data$tooltip),
    stackgroups = TRUE, 
    binwidth = 1, 
    method = "histodot") +
  scale_y_continuous(NULL, 
                     breaks = NULL)
girafe(
  ggobj = p,
  width_svg = 8,
  height_svg = 8*0.618
)
```

::: callout-note
## How to achieve interactivity?

Use the interactive version of `ggplot2` geom functions. Then, use `girafe()` to generate an svg object to be displayed on an html page.

In this example, hovering over data points reveal the student's name and class for that data point.
:::

::: callout-note
## Further customization

`ggiraph` objects can be customized via `options =` and `opts_tooltip()` by adding css declarations.
:::

You can also display statistics on tooltips!

```{r}
tooltip <- function(y, ymax, accuracy = .01) {
  mean <- scales::number(y, accuracy = accuracy)
  sem <- scales::number(ymax - y, accuracy = accuracy)
  paste("Mean maths scores:", mean, "+/-", sem)
}

gg_point <- ggplot(data=exam_data, 
                   aes(x = RACE),
) +
  stat_summary(aes(y = MATHS, 
                   tooltip = after_stat(  
                     tooltip(y, ymax))),  
    fun.data = "mean_se", 
    geom = GeomInteractiveCol,  
    fill = "light blue"
  ) +
  stat_summary(aes(y = MATHS),
    fun.data = mean_se,
    geom = "errorbar", width = 0.2, size = 0.2
  )

girafe(ggobj = gg_point,
       width_svg = 8,
       height_svg = 8*0.618)
```

## Data_id aesthetic

```{r}
p <- ggplot(data=exam_data,
       aes(x = MATHS)) +
  geom_dotplot_interactive(              
    aes(tooltip = CLASS, 
        data_id = CLASS),              
    stackgroups = TRUE,                  
    binwidth = 1,                        
    method = "histodot") +               
  scale_y_continuous(NULL,               
                     breaks = NULL)
girafe(                                  
  ggobj = p,                             
  width_svg = 6,                         
  height_svg = 6*0.618
)                                                                     
```

::: callout-note
## Interactivity

Elements associated with a certain `data_id` will be highlighted when your cursor hovers over a data point with that `data_id`. In this example, this was achieved in addition to the tooltip aesthetic (that will display the `data_id`).
:::

## Onclick aesthetic

`onclick` can be used to hyperlink to other websites on the Internet.

```{r}
exam_data$onclick <- sprintf("window.open(\"%s%s\")",
"https://www.moe.gov.sg/schoolfinder?journey=Primary%20school",
as.character(exam_data$ID))

p <- ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_dotplot_interactive(              
    aes(onclick = onclick),              
    stackgroups = TRUE,                  
    binwidth = 1,                        
    method = "histodot") +               
  scale_y_continuous(NULL,               
                     breaks = NULL)
girafe(                                  
  ggobj = p,                             
  width_svg = 6,                         
  height_svg = 6*0.618)                               
```

::: callout-important
## Javascript instructions

Note the additional column created in the dataset `exam_data` called `onclick` that specifies the javascript to open a window with the given URL. This is necessary to make `onclick` work!
:::

## Coordinating between two plots

`patchwork` can be used with what we have learnt today as well! The two plots will show the data points with the same `data_id` upon cursor hover:

```{r}
p1 <- ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_dotplot_interactive(              
    aes(data_id = ID,
        tooltip = ID),              
    stackgroups = TRUE,                  
    binwidth = 1,                        
    method = "histodot") +  
  coord_cartesian(xlim=c(0,100)) + 
  scale_y_continuous(NULL,               
                     breaks = NULL)

p2 <- ggplot(data=exam_data, 
       aes(x = ENGLISH)) +
  geom_dotplot_interactive(              
    aes(data_id = ID,
        tooltip = ID),              
    stackgroups = TRUE,                  
    binwidth = 1,                        
    method = "histodot") + 
  coord_cartesian(xlim=c(0,100)) + 
  scale_y_continuous(NULL,               
                     breaks = NULL)

girafe(code = print(p1 + p2), 
       width_svg = 6,
       height_svg = 3,
       options = list(
         opts_hover(css = "fill: #202020;"),
         opts_hover_inv(css = "opacity:0.2;")
         )
       ) 
```

## Using plotly methods to achieve interactive data visualization

There are two ways of doing this:

-   `plot_ly()`

-   `ggplotly()`

::: panel-tabset
#### plot_ly()

```{r, echo = FALSE, message = FALSE}
plot_ly(data = exam_data, 
        x = ~ENGLISH, 
        y = ~MATHS, 
        color = ~RACE)
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE}
plot_ly(data = exam_data, 
        x = ~ENGLISH, 
        y = ~MATHS, 
        color = ~RACE)
```
:::

::: panel-tabset
#### ggplotly()

```{r, echo = FALSE, message = FALSE}
p <- ggplot(data=exam_data, 
            aes(x = MATHS,
                y = ENGLISH,
                color = RACE)) +
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))
ggplotly(p)
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE}
p <- ggplot(data=exam_data, 
            aes(x = MATHS,
                y = ENGLISH,
                color = RACE)) +
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))
ggplotly(p)
```
:::

You can achieve a coordinated linked plot using `highlight_key()` and `subplot()` to place the plots side by side.

::: panel-tabset
#### plot_ly()

```{r, echo = FALSE, message = FALSE}
plot_ly(data = exam_data, 
        x = ~ENGLISH, 
        y = ~MATHS, 
        color = ~RACE)
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE}
plot_ly(data = exam_data, 
        x = ~ENGLISH, 
        y = ~MATHS, 
        color = ~RACE)
```
:::

::: panel-tabset
#### Plot

```{r, echo = FALSE, message = FALSE}
d <- highlight_key(exam_data)
p1 <- ggplot(data=d, 
            aes(x = MATHS,
                y = ENGLISH)) +
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))

p2 <- ggplot(data=d, 
            aes(x = MATHS,
                y = SCIENCE)) +
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))
subplot(ggplotly(p1),
        ggplotly(p2))
```

#### Code

```{r, results = 'hide', fig.show = 'hide', message = FALSE}
d <- highlight_key(exam_data)
p1 <- ggplot(data=d, 
            aes(x = MATHS,
                y = ENGLISH)) +
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))

p2 <- ggplot(data=d, 
            aes(x = MATHS,
                y = SCIENCE)) +
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))
subplot(ggplotly(p1),
        ggplotly(p2))
```
:::

## Using crosstalk methods

Example of usage below:

```{r, message = FALSE}
d <- highlight_key(exam_data) 
p <- ggplot(d, 
            aes(ENGLISH, 
                MATHS)) + 
  geom_point(size=1) +
  coord_cartesian(xlim=c(0,100),
                  ylim=c(0,100))

gg <- highlight(ggplotly(p),        
                "plotly_selected")  

crosstalk::bscols(gg,               
                  DT::datatable(d), 
                  widths = 5)        
```

