---
title: "Week 1: Hands-on Exercise"
sidebar: false
pagetitle: "Hands-on Ex 01"
---

::: callout-note
## Disclaimer

Hands-on exercises are for my own practice and are ungraded. Thus, the plots and write-ups may be unrefined and poorly labelled.
:::

Let's explore the ggplot2 package in R!

```{r, include = FALSE}
pacman::p_load(tidyverse)
```

## Load dataset

```{r}
exam_data <- read_csv("data_01/Exam_data.csv")
```

## Comparing R graphics with ggplot2

::: panel-tabset
#### R graphics

```{r}
hist(exam_data$MATHS)

```

#### ggplot2

```{r}
ggplot(data=exam_data, aes(x = MATHS)) +
  geom_histogram(bins=10, 
                 boundary = 100,
                 color="black", 
                 fill="grey") +
  ggtitle("Distribution of Maths scores")
```
:::

::: callout-note
## ggplot2 has a more complicated syntax, but offers much more customization options to help you make your data visualizations beautiful.
:::

## Exploring ggplot2

::: panel-tabset
#### Bar chart

```{r}
ggplot(data = exam_data,
       aes(x = RACE)) +
  geom_bar()
```

#### Dot plot

```{r}
ggplot(data = exam_data,
       aes(x = MATHS)) +
  geom_dotplot(dotsize = 0.5,
               binwidth = 2.5) +
  scale_y_continuous(NULL,
                     breaks = NULL)
```

#### Histogram

```{r}
ggplot(data = exam_data,
       aes(x = MATHS,
           fill = GENDER)) +
  geom_histogram(bins = 20,
                 color = "grey20") +
  scale_fill_manual(values = c("pink", "steelblue"))
```

#### Kernel density

```{r}
ggplot(data = exam_data,
       aes(x = MATHS,
           color = GENDER)) +
  geom_density()
```

#### Box plot

```{r}
ggplot(data = exam_data,
       aes(y = MATHS,
           x = GENDER,
           fill = GENDER)) +
  geom_boxplot(notch = TRUE) +
  scale_fill_manual(values = c("pink", "steelblue"))
```

#### Violin plot

```{r}
ggplot(data = exam_data,
       aes(y = MATHS,
           x = GENDER)) +
  geom_violin()
```

#### Scatterplot

```{r}
ggplot(data = exam_data,
       aes(x = MATHS,
           y = ENGLISH)) +
  geom_point() +
  coord_cartesian(xlim = c(0, 100),
                  ylim = c(0, 100))
```
:::

## Some other elements...

#### Combining geom objects + stat

```{r}
ggplot(data = exam_data,
       aes(y = MATHS,
           x = GENDER,
           fill = GENDER)) +
  geom_boxplot(notch = TRUE) +
  geom_point(position = "jitter",
             size = 0.5) +
  scale_fill_manual(values = c("pink", "steelblue")) +
  stat_summary(geom = "point",
               fun = "mean",
               colour = "red",
               size = 4) +
  theme_classic()
```

::: callout-note
## Theme used: Classic
:::

#### Scatterplot with best fit line!

```{r}
ggplot(data = exam_data,
       aes(x = MATHS,
           y = ENGLISH)) +
  geom_point() +
  geom_smooth(method = lm,
              linewidth = 0.5)
```

#### Working with facets

```{r}
ggplot(data = exam_data,
       aes(x = MATHS)) +
  geom_histogram(bins = 20) +
  facet_wrap(~ CLASS) +
  theme_minimal()
```

::: callout-caution
## Theme used: Minimal
:::

And that's it for Week 1!
